Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2024-12-10 main.tex
update the geometric transformation estimates

\begin{lemma}\label{lemma:startopology}
    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
    Suppose that $1 \leq n \leq 3$. Then the following holds:
    \begin{itemize}
        \item
        If $S \in \calT$ is an inner simplex, 
        then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
        \item
        If $S \in \calT$ is a boundary subsimplex, 
        then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
    \end{itemize}
\end{lemma}
\begin{proof}
    The lemma is obvious if $n = 1$, so we assume $n \geq 2$ in what follows. 
    We prove these statements in several steps. 
    The reader is assumed to have some background in topology. 
    \begin{enumerate}
    \item 
    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with barycenter $z_{S}$, and dimension $k$.
    Let $\calS := \patch_{\calT}(S)$ be its star. 
    Each $l$-dimensional simplex $T \in \calS$ that contains $S$ 
    has vertices $v_0$, $v_1$, $\dots$, $v_k$, $v_{k+1}^{S}$, $\dots$, $v_{l}^{S}$. 
    For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
    $v_0$, $\dots$, $v_{i-1}$, $z_{S}$, $v_{i+1}$, $\dots$, $v_k$, $v_{k+1}^{S}$, $\dots$, $v_{l}^{S}$.
    % \begin{align*}
        % v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}. 
    % \end{align*}
    The collection $\calS'$ of these simplices and their subsimplices constitute a simplicial complex 
    that triangulates the same underlying set as $\calS$.
    Moreover, $\calS' = \patch_{\calS'}(z_{S})$. 
    In particular, $z_{S}$ is a boundary vertex of $\calS'$ if and only if $S$ is a boundary simplex of $\calS$. 
    So it remains to study the topology of vertex stars.

@@

%     If $z$ is an inner vertex of $\calS'$, 
%     then the boundary simplices of $\calS'$,

@@

%     Now suppose that $z$ is a boundary vertex of $\calS'$,

@@

We now provide the desired bi-Lipschitz transformation:
on the one hand, the nonlinear reflection across the interface between the selected simplex and the remainder of the local star,
and on the other hand, the bi-Lipschitz contraction from the local star onto the complement of the selected simplex. 
We give detailed estimates for the singular values of their Jacobians.

\begin{proposition}\label{proposition:starreflection}
    Let $\calT$ be a triangulation of an $n$-dimensional domain. 
    Let $S \in \calT$ be an inner simplex of dimension $k < n$,
    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
    and let 
    \begin{align*}
        \Makoto := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
        \qquad 
        {\Gamma_1} := \Makoto \cap T,
        \qquad 
        {\Gamma_2} := \overline{ \partial T \setminus \partial \Makoto }.
    \end{align*}
    The following holds, where the constants on the right-hand sides are as stated in the proof. 
    \begin{enumerate}
    \item 
    There exists a bi-Lipschitz piecewise affine mapping
    \begin{align*}
        \Xi_{1} : T \rightarrow \Makoto
    \end{align*}
    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
    \begin{gather*}
        \sigma_1 \leq \Cfive{n}{k}(\calT),
        \quad 
        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{k}(\calT),
        \quad 
        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
        \\
        \sigma_n \leq \Csechs{n}{k}(\calT),
        \quad 
        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{k}(\calT),
        \quad 
        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
    \end{gather*}
%     and which satisfies the upper bounds 
%     \begin{gather*}
%         \matnorm{ \Jacobian\Xi_{1} }          \leq \Cfive{n}{k}(\calT),
%         \quad 
%         \matnorm{ \Jacobian\Xi_{1}^{-1} }     \leq \Csechs{n}{k}(\calT),
%         \\
%         | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
%         \quad 
%         | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
%     \end{gather*}
    \item 
    There exists a bi-Lipschitz piecewise affine mapping
    \begin{align*}
        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Makoto
    \end{align*}
    which is the identity along $\partial \Makoto \setminus \partial T$.
    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
    \begin{gather*}
        \sigma_1 \leq \Csieb{n}{k}(\calT),
        \quad 
        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{k}(\calT),
        \quad 
        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
        \\
        \sigma_n \leq \Cacht{n}{k}(\calT),
        \quad 
        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{k}(\calT),
        \quad 
        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
    \end{gather*}
%     and which satisfies the upper bounds 
%     \begin{gather*}
%         \matnorm{ \Jacobian\Xi_{2} }          \leq \Csieb{n}{k}(\calT),
%         \quad 
%         \matnorm{ \Jacobian\Xi_{2}^{-1} }     \leq \Cacht{n}{k}(\calT),
%         \\
%         | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
%         \quad 
%         | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
%     \end{gather*}
    \end{enumerate}
\end{proposition}
\begin{proof}
    We derive the estimate in several steps. 
    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
    \begin{itemize}
        \item 
        Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
        % Let $I := \Makoto \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
        Note that ${\Gamma_2}$ is the union of exactly those faces of $T$ that contain $S'$,
        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$.

        \item 
        We let $z'_{S}$ be the midpoint of $S'$. 
        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calS$. 
        Obviously, all $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.

        We define another simplicial complex $\calS^c$ as follows:
        given any $n$-simplex $K \in \calS$, 
        we replace its vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
        thus obtaining a new simplex $K'$. 
        Indeed, that $\calS^c$ is a simplicial complex follows easily from $\calS$ being a simplicial complex.

        We let the simplicial complex $\calS'$ be the union of $\calS$ and $\calS^c$. 
        By construction, all its $n$-simplices contain $S$ as a subsimplex,
        % Indeed, $\calS'$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
        Moreover, $S$ is an inner subsimplex of that triangulation. 
        In particular, $\calS'$ is its own star around $S$.

        % TODO Check that $\calS'$ is a triangulation

        \item 
        As additional step, we introduce another simplicial complex $\calR'$ from $\calS'$ via barycentric subdivision of $S$.
        Then $\calR'$ is its own local star around the barycenter $z_S$.
        In particular, all $n$-simplices in $\calR'$ contain $z_{S}$. 
        The simplicial complex $\calR'$ also contains as subcomplexes the corresponding refinements of $\calS$ and $\calS^{c}$, 
        which we denote by $\calR$ and $\calR^{c}$, respectively.

@@

        We introduce a new mapping $\Theta : \underlying{\calR} \rightarrow \underlying{\calR^c}$ between the underlying sets as follows.
        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$

@@

        that agree on the vertices common to $K$ and $K'$.

@@

            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
        % Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
        %     \matnorm{ \Jacobian \Theta_{|K}      } &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \geometricshapemeasure(A_{K}),
        %     \matnorm{ \Jacobian \Theta_{|K}^{-1} } &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \geometricshapemeasure(A_{K}).

@@

            |\det( \Jacobian      \Theta_{|K} )|
            |\det( \Jacobian^{-1} \Theta_{|K} )|

@@

        We $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.

@@

            \Theta_{|K}(x) 

@@

            \Theta_{|K}( h_{z} ) 

@@

        Evidently, the transformation $\Theta_{|K}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 

@@

            B 

@@

        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
        Its square roots are the desired singular values of $B$:

@@

            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}

@@

        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,

@@

        Recall that $K \in \calR$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
        Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
        which must be contained in some face of $T$. 
        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of that face of $T$. 
        Thus 
        \begin{align*}
            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
            = 
            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            = 
            \frac{ \vecnorm{ z_{S'} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            \leq 
            (n-k) \aspectratio(T)
%             = 
%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
%             \leq 
%             \frac{ n-k }{n!}
%             \cdot 
%             \frac{ \diam(T)^{n} }{ \vol(T) }
            .
        \end{align*}
        This establishes bounds on the singular values of the transformation. 
        We abbreviate 
        \begin{align}\label{math:upper_bound_for_theta}
            B_{T} 
            := 
%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
%             \geq 
            \sqrt{ 
                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
            } 
            + 
            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
            .
        \end{align}

        \item 
        We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Theta$.
        We construct a bi-Lipschitz mapping 
        \begin{align*}
            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}.
        \end{align*}
        The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
        which will be the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.

        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
        Here, we let $Q \subseteq K \cap K^{c}$ be the subsimplex 
        that is complementary to the line segment from the origin to $z_{S'}$ in $K$.
        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $K^{c}$.
        From the very definition of simplices, we now conclude that any $x \in K \cup K^{c}$ 
        has a unique representation
        \begin{align*}
            x = \lambda z_{S} + \mu x^{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x^{Q} \in Q,
        \end{align*}
        Since $\mu x^{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
        \begin{align*}
            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
            .
        \end{align*}
        Based on that observation, we define 
        \begin{align*}
            \Phi_{K}(x) 
            &
            := 
            \mu x^{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
            \\&
            = 
            x - \left( \frac 3 2 \lambda(x) - \frac 1 2 \right) z_{S'}
            = 
            x - \left( \frac 3 2 \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - \frac 1 2 \right) z_{S'}
            .
        \end{align*}
        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
        that satisfies the desired mapping properties. 
        It remains to analyze its Jacobian to get explicit estimates.

@@

            \Jacobian \Phi_{K}(x)

@@

            C 

@@

        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
            \sigma_{\max} 

@@

            \sigma_{\min} 

@@

            \sigma_{\max} 

@@

        Notice that $\sigma_{\max} \sigma_{\min} = 1/2$. 

@@

        Hence, these are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. Therefore,

@@

        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.

@@

        We conclude that 

@@

            \matnorm{ \Jacobian\Phi_{K} } 

@@

            \matnorm{ \Jacobian\Phi_{K}^{-1} } 

@@

            \Psi : \underlying{\calR'} \rightarrow \underlying{\calK}.
        Recall that $\calR'$ and $\calK$ are their own respective stars around the origin,

@@

        Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$. We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively. They define respective hyperplanes $H_{G}$ and $H_{K}$,

@@

            \matnorm{ \Jacobian\Psi(x) }

@@

            \matnorm{ \Jacobian\Psi(z)^{-1} }

@@

@@

            \det\Jacobian\Psi^{-1}(x)

@@

        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calR$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
        In the case $G \in \calR^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$

>>>>

\begin{lemma}\label{lemma:startopology}
    Let $\calT$ be a finite $n$-dimensional simplicial complex whose underlying space is a manifold $\calM$.
    Suppose that $1 \leq n \leq 3$. Then the following holds:
    \begin{itemize}
        \item
        If $S \in \calT$ is an inner simplex, 
        then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as an inner simplex
        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-sphere. 
        \item
        If $S \in \calT$ is a boundary subsimplex, 
        then $\patch_{\calT}(S)$ is a simplicial $n$-ball with $S$ as a boundary simplex,
        and $\carapace_{\calT}(S)$ is a simplicial $(n-1)$-ball.
    \end{itemize}
\end{lemma}
\begin{proof}
    The lemma is obvious if $n = 1$, so we assume $n \geq 2$ in what follows. 
    We prove these statements in several steps. 
    The reader is assumed to have some background in topology. 
    \begin{enumerate}
    \item 
    Let $S$ be any simplex with vertices $v_0, v_1, \dots, v_k$, with barycenter $z_{S}$, and dimension $k$.
    Let $\calS := \patch_{\calT}(S)$ be its star. 
    Each $l$-dimensional simplex $T \in \calS$ that contains $S$ 
    has vertices $v_0$, $v_1$, $\dots$, $v_k$, $v_{k+1}^{S}$, $\dots$, $v_{l}^{S}$. 
    For any such simplex, we introduce a decomposition $T_{0}, \dots, T_{k}$, where each $T_{i}$ has vertices 
    $v_0$, $\dots$, $v_{i-1}$, $z_{S}$, $v_{i+1}$, $\dots$, $v_k$, $v_{k+1}^{S}$, $\dots$, $v_{l}^{S}$.
    % \begin{align*}
        % v_0, \dots, v_{i-1}, z_{S}, v_{i+1}, \dots, v_k, v_{k+1}^{S}, \dots, v_{l}^{S}. 
    % \end{align*}
    The collection $\calS^\ast$ of these simplices and their subsimplices constitute a simplicial complex 
    that triangulates the same underlying set as $\calS$.
    Moreover, $\calS^\ast = \patch_{\calS^\ast}(z_{S})$. 
    In particular, $z_{S}$ is a boundary vertex of $\calS^\ast$ if and only if $S$ is a boundary simplex of $\calS$. 
    So it remains to study the topology of vertex stars.

@@

%     If $z$ is an inner vertex of $\calS^\ast$, 
%     then the boundary simplices of $\calS^\ast$,

@@

%     Now suppose that $z$ is a boundary vertex of $\calS^\ast$,

@@

\clearpage
We now provide the desired bi-Lipschitz transformation:
on the one hand, the nonlinear reflection across the interface between the selected simplex and the remainder of the local star,
and on the other hand, the bi-Lipschitz contraction from the local star onto the complement of the selected simplex. 
We give detailed estimates for the singular values of their Jacobians.

\begin{proposition}\label{proposition:starreflection}
    Let $\calT$ be a triangulation of an $n$-dimensional domain. 
    Let $S \in \calT$ be an inner simplex of dimension $k < n$,
    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
    and let 
    \begin{align*}
        \Makoto := \overline{ \underlying{\patch_{\calT}(S)} \setminus T },
        \qquad 
        {\Gamma_1} := \Makoto \cap T,
        \qquad 
        {\Gamma_2} := \overline{ \partial T \setminus \partial \Makoto }.
    \end{align*}
    The following holds, where the constants on the right-hand sides are as stated in the proof. 
    \begin{enumerate}
    \item 
    There exists a bi-Lipschitz piecewise affine mapping
    \begin{align*}
        \Xi_{1} : T \rightarrow \Makoto
    \end{align*}
    which is the identity along ${\Gamma_1} = T \cap \Makoto$. 
    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
    \begin{gather*}
        \sigma_1 \leq \Cfive{n}{k}(\calT),
        \quad 
        \sigma_2,\dots,\sigma_n \leq \Cfiveprime{n}{k}(\calT),
        \quad 
        | \det\Jacobian\Xi_{1} |      \leq \Cdetfive{n}{k}(\calT),
        \\
        \sigma_n^{-1} \leq \Csechs{n}{k}(\calT),
        \quad 
        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Csechsprime{n}{k}(\calT),
        \quad 
        | \det\Jacobian\Xi_{1}^{-1} | \leq \Cdetsechs{n}{k}(\calT).
    \end{gather*}
    \item 
    There exists a bi-Lipschitz piecewise affine mapping
    \begin{align*}
        \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow \Makoto
    \end{align*}
    which is the identity along $\partial \Makoto \setminus \partial T$.
    At any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of its Jacobian satisfy 
    \begin{gather*}
        \sigma_1 \leq \Csieb{n}{k}(\calT),
        \quad 
        \sigma_2,\dots,\sigma_n \leq \Csiebprime{n}{k}(\calT),
        \quad 
        | \det\Jacobian\Xi_{2} |      \leq \Cdetsieb{n}{k}(\calT),
        \\
        \sigma_n^{-1} \leq \Cacht{n}{k}(\calT),
        \quad 
        \sigma_1^{-1},\dots,\sigma_{n-1}^{-1} \leq \Cachtprime{n}{k}(\calT),
        \quad 
        | \det\Jacobian\Xi_{2}^{-1} | \leq \Cdetacht{n}{k}(\calT).
    \end{gather*}
    \end{enumerate}
\end{proposition}
\begin{proof}
    We derive the estimate in several steps. 
    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
    \begin{itemize}
        \item 
        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin. 
        % Let $I := \Makoto \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        %We let ${\Gamma_2} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        %So ${\Gamma_2$} is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$.
        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$.

        \item 
        We let $z_{S'}$ be the midpoint of $S'$. 
        We apply barycentric refinement to the complementary simplex $S'$, which produces a new triangulation $\calD$ of the underlying set $\underlying{T}$. 
        Obviously, all $n$-simplices in $\calD$ contain $S$ and $z_{S'}$.

        We define another simplicial complex $\calD^c$ as follows:
        given any $n$-simplex $K \in \calD$, 
        we replace its vertex $z_{S}'$ by the new vertex $-z_{S}'$ at the opposite position,
        thus obtaining a new simplex $K^{c}$. 
        Indeed, that $\calD^c$ is a simplicial complex follows easily from $\calD$ being a simplicial complex.

        We let the simplicial complex $\calD^\ast$ be the union of $\calD$ and $\calD^c$. 
        By construction, all its $n$-simplices contain $S$ as a subsimplex,
        % Indeed, $\calD^\ast$ is indeed a triangulation since they are disjoint except for their proper subsimplices. 
        Moreover, $S$ is an inner subsimplex of that triangulation. 
        In particular, $\calD^\ast$ is its own star around $S$.

        % TODO Check that $\calD^\ast$ is a triangulation

        \item 
        As additional step, we introduce another simplicial complex $\calG^\ast$ from $\calD^\ast$ via barycentric subdivision of $S$.
        Then $\calG^\ast$ is its own local star around the barycenter $z_S$.
        In particular, all $n$-simplices in $\calG^\ast$ contain $z_{S}$. 
        The simplicial complex $\calG^\ast$ also contains as subcomplexes the corresponding refinements of $\calD$ and $\calD^{c}$, 
        which we denote by $\calG$ and $\calG^{c}$, respectively.
        Given any $n$-simplex in $\calG$, replacing its vertex $z_{S}$ with its opposite $-z_{S}$ gives an associated $n$-simplex in $\calG^{c}$.

@@

        % Notice that $A_{G^{c}}$ and $A_{G}$ have the same singular values. Thus
        %     \matnorm{ \Jacobian \Theta_{|G}      } &\leq \| A_{G^{c}} \| \cdot \| A_{G}^{-1} \| \leq \geometricshapemeasure(A_{G}),
        %     \matnorm{ \Jacobian \Theta_{|G}^{-1} } &\leq \| A_{G^{c}}^{-1} \| \cdot \| A_{G} \| \leq \geometricshapemeasure(A_{G}).
        We introduce a new mapping $\Theta : \underlying{\calG} \rightarrow \underlying{\calG^c}$ between the underlying sets as follows.
        Let $G \in \calG$ be an $n$-simplex and $G^{c} \in \calG^{c}$ be constructed from $G$.
        We let $A_{G} : \Delta^{n} \rightarrow G$ and $A_{G^{c}} : \Delta^{n} \rightarrow G^{c}$

@@

        that agree on the vertices common to $G$ and $G^{c}$.

@@

            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}

@@

            |\det( \Jacobian      \Theta_{|G} )|
            |\det( \Jacobian^{-1} \Theta_{|G} )|

@@

        We $h_{z} \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $G$.

@@

            \Theta_{|G}(x) 

@@

            \Theta_{|G}( h_{z} ) 

@@

        Evidently, the transformation $\Theta_{|G}$ equals the identity on the orthogonal complement of the span of $h_{z}$ and $b_{z}$. 

@@

            M_{\Theta,G} 

@@

        We compute the eigenvalues of the symmetric matrix $M_{\Theta,G}^{\ast} M_{\Theta,G}$. 
        Its square roots are the desired singular values of $M_{\Theta,G}$:

@@

            \sigma_{\max}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta) \label{math:theta_max}
            \sigma_{\min}(\Theta,G) := \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) \label{math:theta_min}

@@

        We conclude that these two are also the maximal and minimal singular values of $\Jacobian\Theta_{|G}$,

@@

        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
        which must be contained in some face of $T$. 
        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of that face of $T$. 
        Thus 
        \begin{align*}
            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
            = 
            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            = 
            \frac{ \vecnorm{ z_{S'} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            \leq 
            (n-k) \aspectratio(T)
%             = 
%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
%             \leq 
%             \frac{ n-k }{n!}
%             \cdot 
%             \frac{ \diam(T)^{n} }{ \vol(T) }
            .
        \end{align*}
        This establishes bounds on the singular values of the transformation. 
        We abbreviate 
        \begin{align}\label{math:upper_bound_for_theta}
            \mu_{T,k} 
            := 
%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
%             \geq 
            \sqrt{ 
                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
            } 
            + 
            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
            .
        \end{align}
        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
        \begin{align}
            \sigma_{1}(\Theta,x) \leq \mu_{T,k},
            \quad 
            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
            \quad 
            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,k}.
        \end{align}
        \item 
        We introduce another mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$ as follows. 
        Consider any $n$-simplex $G \in \calG$ and let $G^c \in \calG^{c}$ be its image under $\Theta$.
        We construct a bi-Lipschitz mapping 
        \begin{align*}
            \Phi_{G} : G \cup G^{c} \rightarrow G^{c}.
        \end{align*}
        The construction will be such that the union of $\Phi_{G}$ for all $n$-simplices $G \in \calG$
        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calG^\ast} \rightarrow \underlying{\calG^{c}}$,
        which will be the identity along $\partial\underlying{\calG^\ast} \setminus \partial\underlying{\calG}$.

        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $G^{c}$.
        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
        has a unique representation
        \begin{align*}
            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
        \end{align*}
        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
        \begin{align*}
            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
            .
        \end{align*}
        Based on that observation, we define 
        \begin{align*}
            \Phi_{G}(x) 
            &
            := 
            \mu x_{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
            \\&
            = 
            x - \left( \frac 3 2 \lambda(x) - \frac 1 2 \right) z_{S'}
            = 
            x - \left( \frac 3 2 \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - \frac 1 2 \right) z_{S'}
            .
        \end{align*}
        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
        that satisfies the desired mapping properties. 
        It remains to analyze its Jacobian to get explicit estimates.

@@

            \Jacobian \Phi_{G}(x)

@@

            M_{\Phi,G} 

@@

        By building the symmetric matrix $M_{\Phi,G}^{t} M_{\Phi,G}$ and computing its eigenvalues, 
        we obtain the singular values 
            \sigma_{\max}(\Phi,G) 

@@

            \sigma_{\min}(\Phi,G)

@@

            \sigma_{\max}(\Phi,G) 

@@

@@

        Hence, these are also the maximal and minimal singular values of the Jacobian $\Jacobian \Phi_{G}$, the remaining singular values being equal to $1$. 
        Notice that $\sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = 1/2$. 
        Therefore,

@@

        We now recall that the height of $h_{z}$ in $G \in \calG$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.

@@

        We conclude that the singular values of the Jacobian of $\Phi$ at almost every $x$ satisfy 

@@

            \sigma_{1}(\Phi,x) % \matnorm{ \Jacobian\Phi_{G} } 

@@

            \sigma_{2}(\Phi,x) = \dots = \sigma_{n-1}(\Phi,x) = 1,
            \sigma_{n}(\Phi,x)^{-1} % \matnorm{ \Jacobian\Phi_{G}^{-1} } 

@@

            \Psi : \underlying{\calG^\ast} \rightarrow \underlying{\calK}.
        Recall that $\calG^\ast$ and $\calK$ are their own respective stars around the origin,

@@

        Let ${G} \in \calG^\ast$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$. We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively. They define respective hyperplanes $H_{G}$ and $H_{K}$,

@@

            % \matnorm{ \Jacobian\Psi(x) }
            \sigma_{1}( \Jacobian\Psi(x) )

@@

            % \matnorm{ \Jacobian\Psi(z)^{-1} }
            \sigma_{1}( \Jacobian\Psi(z)^{-1} )

@@

            \sigma_{2}( \Jacobian\Psi(x) ) = \dots = \sigma_{n-1}( \Jacobian\Psi(x) )

@@

            \det\Jacobian\Psi^{-1}(z)

@@

        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calG$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
        In the case $G \in \calG^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
